---
title: "Graphic Description"
description: |
  In this article, I treat of the **sea urchin biometry**. I chose this dataset because it has a large number of variables (19). 
  The sea urchins studied have two origins: one part comes from ***culture***, and the other from ***fishery***.
author:
  - name: François Fokan
    url: {}
date: 11-18-2020
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Graphic
```{r}
SciViews::R

data <- read("urchin_bio", package = "data.io")

chart(urchin_bio, spines ~ sex %fill=% origin) +
  geom_boxplot(na.rm = TRUE)
```

On this graph, we see that, despite their origin or their sex, the dry weight *(in g)* of calcareous parts of the spines is relatively the same in all individuals.

However, there are some slight differences. **For males**, the individuals from culture have the highest dry weight of the spines, and **for females**, it is the individuals from fishery who have the highest dry weight of the spines.

****

Learn more about using Distill at <https://rstudio.github.io/distill>.

